Model LF

### 2022-10-01 max_dp endogen stød.Rmd
Commit sensitivitet

@@

#### Sensitivity analysis variables 
sens1=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> wage_gap1 > 0.4 & SD1 >=1 & shock_wage_ds_model > 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/0.6
IF> wage_gap1 <= 0.4 & SD1 >=1 & shock_wage_ds_model > 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

@@

   sens1 = TIMESERIES(c(sens1),   
                       START=c(2005,2),FREQ=4),

  ## max_dp

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4)
)
```

@@

#S_modelData$u_ds = u_ds

@@

## Scenario 1 max_dp

@@

## Scenario 1 wage_ds_t

@@

## Scenario 2 part

@@

## Scenario 3 kuld

We will now look at one of the scenarios where the changes in regulation determined in "skattereformen 2012" was not conducted

@@

```{r}
# Define add-factor list (defining shock)
constantAdjList3 <- list(

  shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_3 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList3
                    )
```

yk_ds_03 = Shock_3$simulation$yk_ds
emp_03 = Shock_3$simulation$emp
wage_ds_03 = Shock_3$simulation$wage_ds
ur_ds_03 = Shock_3$simulation$ur_ds
pc_ds_03 = Shock_3$simulation$pc_ds
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
pconk_ds_03 = Shock_3$simulation$pconk_ds
komp_r_03 = Shock_3$simulation$komp_r
max_dp_03 = Shock_3$simulation$max_dp
nben_h_03 = Shock_3$simulation$nben_h
yd_hk_ds_03 = Shock_3$simulation$yd_hk_ds
ik_03 = Shock_3$simulation$ik

wage_ds_t_03 = Shock_3$simulation$wage_ds_t

wage_ds_t_03 = Shock_3$simulation$wage_ds_t

nben_h_un_03 = Shock_3$simulation$nben_h_un

nl_g_03 = Shock_3$simulation$nl_g

nsben_h_03 = Shock_3$simulation$nsben_h

plot(komp_r_03, col= "red"); lines(komp_r_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nben_h_un_03, col= "red"); lines(nben_h_un_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yk_ds_03, col= "red", main= "Yk_ds"); lines(yk_ds_01, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(ur_ds_03, col= "red"); lines(ur_ds_02, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_03, col= "red"); lines(wage_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(pc_ds_03, col= "red"); lines(pc_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(yd_hk_ds_03, col= "red"); lines(yd_hk_ds_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

# The last one doesnt fit the working paper, but fits the model used for this replication

plot(max_dp_03, col= "red"); lines(max_dp_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_ds_t_03, col= "red"); lines(wage_ds_t_02, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(nsben_h_03, col= "red"); lines(nsben_h_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

## Scenario 4 all shocks

@@

## Scenario 5 reg wage

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds
u_ds_05 = Shock_5$simulation$u_ds

gk_05 = Shock_5$simulation$gk

## Scenario 6 reg part

## Scenario 7 reg all

@@

>>>>

max_gap= ts(c(0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4,0.4), start = c(2005, 2), end =  c(2020,1), frequency = 4)

@@

#### Sensitivity analysis variables 
sens1=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)
sens2=ts(0,start = c(2005,2), end = c(2020,1), frequency = 4)

@@

COMMENT> Sensitivitets analyse
IDENTITY> sens2
EQ> sens2 = sens2*1

@@

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> wage_gap1 > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> wage_gap1 <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

@@

COMMENT> lavet mhs til sensitivitets analyse
IDENTITY> max_gap
EQ> max_gap = 0.4
IF> sens2 <= 0
IDENTITY> max_gap
EQ> max_gap = 0.38
IF> sens2 > 0

@@

   sens1 = TIMESERIES(c(sens1),   
                       START=c(2005,2),FREQ=4),
  sens2 = TIMESERIES(c(sens2),   
                       START=c(2005,2),FREQ=4),
  ## max_dp

@@

  shock_1_model  = TIMESERIES(c(shock_1_model ),   
                           START=c(2005,2),FREQ=4),
  shock_2_model  = TIMESERIES(c(shock_2_model ),   
                           START=c(2005,2),FREQ=4),
  shock_3_model  = TIMESERIES(c(shock_3_model ),   
                           START=c(2005,2),FREQ=4),
  shock_kuld_model  = TIMESERIES(c(shock_kuld_model),   
                           START=c(2005,2),FREQ=4),
   pf_shock = TIMESERIES(c(pf_shock),   
                        START=c(2005,2),FREQ=4),
  g_shock = TIMESERIES(c(g_shock),   
                        START=c(2005,2),FREQ=4),
  pm_ds_shock = TIMESERIES(c(pm_ds_shock),   
                        START=c(2005,2),FREQ=4),
  iloan_shock = TIMESERIES(c(iloan_shock),   
                        START=c(2005,2),FREQ=4),
  idep_shock = TIMESERIES(c(idep_shock),   
                        START=c(2005,2),FREQ=4),
   ibd_shock = TIMESERIES(c(ibd_shock),   
                        START=c(2005,2),FREQ=4),
  iboa_shock = TIMESERIES(c(iboa_shock),   
                        START=c(2005,2),FREQ=4),
   tax_rate1_shock = TIMESERIES(c(tax_rate1_shock),   
                        START=c(2005,2),FREQ=4),
  wage_gap = TIMESERIES(c(wage_gap),   
                        START=c(2006,2),FREQ=4),
  wage_gap1 = TIMESERIES(c(wage_gap1),   
                        START=c(2006,2),FREQ=4),
  wage_ds_tt = TIMESERIES(c(wage_ds_tt),   
                        START=c(2006,1),FREQ=4),
   max_gap = TIMESERIES(c(max_gap),   
                        START=c(2005,2),FREQ=4)
)
```

@@

#S_modelData$sens2 = sens2

@@

## Scenario 2 reg wage

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds
u_ds_05 = Shock_5$simulation$u_ds
wage_gap1_05 = Shock_5$simulation$wage_gap1
gk_05 = Shock_5$simulation$gk

## Scenario 3 reg part

## Scenario 4 reg all

## Scenario 1.1 max_dp

@@

## Scenario 1.2 wage_ds_t

@@

## Scenario 1.3 part

@@

## Scenario 1.4 all shocks

@@

@@

@@

## Sens 2

We look at a change in the wage-gap that the unions will demand at a wage negotiation.

```{r}
# Define add-factor list (defining shock)
constantAdjList1_sens2 <- list(

 sens2 = TIMESERIES(sens2+1 ,START=c(2006,3),  FREQ='Q'),
 shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q')

```{r}
# Simulate the model (following shock)
sens_2_S1 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList1_sens2
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_s2 = sens_2_S1$simulation$max_dp
wage_s2 = sens_2_S1$simulation$wage
komp_r_s2 = sens_2_S1$simulation$komp_r
part_s2 = sens_2_S1$simulation$part
yk_ds_s2 = sens_2_S1$simulation$yk_ds
pc_ds_s2 = sens_2_S1$simulation$pc_ds
wage_ds_t_s2 = sens_2_S1$simulation$wage_ds_t
pc_ds_s2 = sens_2_S1$simulation$pc_ds
max_gap_s2 = sens_2_S1$simulation$max_gap

wage_gap1_s2 = sens_2_S1$simulation$wage_gap1

```{r}
plot((wage_ds_t_s2/wage_ds_t_00), col= "red", ylim= c(1, 1.1));
lines((wage_ds_t_05/wage_ds_t_00), col="black");
legend("top", legend=c("No suppression",
                       "Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "black"));
grid()
```

```{r}
plot(wage_gap1_s2, col= "red"); lines(wage_gap1_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
